% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{Kevin Shu\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Present Address} \\ 1737 Liberty Parkway NW \\ Atlanta, GA 30318  \\
        (626) 399-3716 }
\address{{\bf Permanent Address} \\ 84 Cheesespring Road \\ Wilton, CT 06897}

 
\begin{resume} 

\section{Education} 
B.S. in Mathematics, Computer Science, California Institute of Technology, Pasadena, CA, June 2018 \\
QPA 3.9
 

\section{Experience}
 {\bf Full-time Software Engineer,} Google, Mountain View, CA \hfill August 2018-July 2019
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Full stack web development for a data labelling service, like Mechanical Turk
 \item Added a major feature for tracking work in the system
 \item Managed roll-outs and infrastructure
 \item Worked with C++, Java.
 \end{itemize}

{\bf Advanced Algorithms Teaching Assistant,} Caltech, Pasadena, CA \hfill Jan 2018-Mar 2018
\begin{itemize} \itemsep -2pt %reduce space between items
\item Graded homework and gave recitations in graduate level algorithms course.
\item Covered multiplicative weights learning, streaming algorithms,
spectral graph theory, semidefinite programming
\end{itemize}
 
{\bf Linear Algebra Teaching Assistant,} Caltech, Pasadena, CA \hfill Sep 2017-Dec 2017
\begin{itemize} \itemsep -2pt %reduce space between items
\item Graded homework for the applied linear algebra course, including topics like linear algebra, including spectral graph theory, polynomial
interpolation, and principal components analysis.
\item Gave 1 hour of office hours per week.
\end{itemize}
 
{\bf Software Engineering Intern,} Google, Mountain View, CA \hfill Aug 2018-Jul 2019
\begin{itemize} \itemsep -2pt %reduce space between items
\item Gathered data from online sources by parsing Reddit pages.
\item Built a machine learning model to provide movie recommendations.
\item Worked with C++, Python.
\end{itemize}
 
{\bf Research in Causality,} Caltech, Pasadena, CA \hfill Aug 2018-Jul 2019
\begin{itemize} \itemsep -2pt %reduce space between items
\item Developed theory of causality and developed bounds on probability distributions.
\item Applied geometric and linear programming in search of bounds.
\end{itemize}

\section{Leadership   Activities} 
               {\bf Senior Class President,} Caltech, Pasadena, CA    \hfill         2018-2019 
        \begin{itemize} \itemsep -2pt
              \item 
		 \end{itemize}

		{\bf Board of Control Secretary,} Caltech \hfill   2017
                \begin{itemize} \itemsep -2pt
                 \item  
		 \end{itemize}

\section{Academic \\ Honors} 
2018 NSFGRP Fellowship Recipient\\

 

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Computer \\ Skills}
   \begin{tabular}{l p{3in}}
    \underline{Languages:} & COBOL, Pascal,C, APL, Basic \\

     \underline{Software:} &  SPIRES, dBase III, Datastar database 
                        systems, GPSS simulation, FCS-EPS financial 
                        planning, SAS statistical analysis, 
                        Lotus1-2-3, MPSX optimization modeling 
 \end{tabular}

\end{resume} 
\end{document} 



